---
title: Summary Document
subtitle: "Report generated: `r format(Sys.time(), '%a/%d/%b %Y')`"
output: html_document
params:
  case_notes: default
  exam_notes: default
  activity: default
  control_substrate: default
  control_shape: default
  control_shed: default
  fibre_type: default
  fibre_colour: default
  transfer_direction: default
  n_fibres: 1000
  recipient_substrate: default
  recipient_shape: default
  recipient_retain: default
  Hp: default
  Hd: default
  alternative_transfer: true
  source_is_x: true
  chosen_scene: default
  LR_formula: default
  tn_assumption: true
  tdn_assumption: true
  system_parameters_all: !r list()
  system_parameters: !r list()
  system_calculation: 0
  user_parameters: !r list()
  user_calculation: 0
  dataset: !r data.frame()

---

# 1. Set up

On Saturday 21st March, Joe Citizen attended a major social function at a prime licensed venue. Shortly after arriving, he exited the venue to retrieve something from his car when he was tackled and assaulted by a man wearing a red hoody. Security and police quickly attended the scene. A few hours later, a man matching the description, Max Mustermann, was taken into custody and his garments including a red hoody and brown chinos were collected. Joe also submitted his yellow Minions T-shirt for examination.

As the forensic scientist tasked with performing analyses and interpreting findings relating to this case, you have recovered a number of foreign fibres from Joes T-shirt.

## Case details

User-entered case notes: `r params$case_notes`

Nature of incident: `r params$activity`

Control substrate: `r params$control_substrate`

Control shape: `r params$control_shape`

Control shed: `r params$control_shed`

## Trace details

Blurb about trace details.

User-entered examination notes: `r params$exam_notes`

Fibre type: `r params$fibre_type`

Fibre colour: `r params$fibre_colour`

Direction of transfer: `r params$transfer_direction`

Number of fibres: `r params$n_fibres`


## Recipient properties

Recipient substrate: `r params$recipient_substrate`

Recipient shape: `r params$recipient_shape`

Recipient retain: `r params$recipient_retain`

## Activity level propositions

Hp: `r params$Hp`

Hd: `r params$Hd`
  
Alternative transfer event: `r params$alternative_transfer`

Source is X: `r params$source_is_x`

## Scene C assumptions

Assume tn >> t0: `r params$tn_assumption`
Assume tdn >> t0: `r params$tdn_assumption`

## Bayes factor

Formula: `r params$LR_formula`


# 2. Results

## System values

System parameters: `r params$system_parameters`
System-calculated LR: `r params$system_calculation`

## User values

User parameters in a list:

```{r echo = FALSE}
parameter_list <- ""

for (param in names(params$user_parameters)) {
  parameter_list <- paste0(parameter_list, param, ": ", params$user_parameters[[param]], "<br>")
}
```

`r parameter_list`

User parameters in a table:

```{r echo=FALSE}
library(knitr)
parameter_table <- data.frame(params$user_parameters)

kable(parameter_table)
```


User-calculated LR: `r params$user_calculation`

## Sensitivity to inputs

```{r}
calculate_LR <- function(calc_params, chosen_scene) {
  with(calc_params,
       if (chosen_scene == "A") {
         (b0 * tn) / (bn * gamma)
       } else if (chosen_scene == "B") {
         (b0 * tn) / (b0 * gamma * tdn)
       } else if (chosen_scene == "C") {
         (b0 * tn + bn * gamma * t0) / (b0 * tdn + bn * gamma * td0)
       } else if (chosen_scene == "C1") {
         (b0 * tn) / (b0 * tdn + bn * gamma * td0)
       } else if (chosen_scene == "C2") {
         tn / tdn
       }
  )
}
```

```{r}
nfibres_range <- seq(from = 201, to = 3000, by = 1)

tn_range <- params$dataset$mean.prob[params$dataset$no.fibres == nfibres_range]

calc_params_system <- params$system_parameters_all
calc_params_user <- params$user_parameters

for (param in names(calc_params_system)) {
  if (!param %in% names(calc_params_user)) {
    calc_params_user[[param]] <- calc_params_system[[param]]
  }
}

calc_params_user$tn <- tn_range
calc_params_system$tn <- tn_range

svty_df <- data.frame()

for (chosen_scene in c("A", "B", "C", "C1", "C2")) {
  
  LR_user_svty <- calculate_LR(calc_params_user, chosen_scene)
  LR_system_svty <- calculate_LR(calc_params_system, chosen_scene)
  
  svty_df <- bind_rows(data.frame(nfibres = nfibres_range, tn = tn_range, 
                                  LR = LR_user_svty, params = "User", scene = chosen_scene),
                       data.frame(nfibres = nfibres_range, tn = tn_range, 
                                  LR = LR_system_svty, params = "System", scene = chosen_scene),
                       svty_df)
}


ggp <- ggplot(data = svty_df, mapping = aes(x = nfibres, y = LR, color = scene, linetype = params)) +
  geom_line() +
  labs(x = "Number of fibres", y = "LR", color = "Scene", linetype = "System/User")

plot(ggp)

svty_df %>%
      plot_ly(x = ~nfibres,
              y = ~LR,
              color = ~scene,
              linetype = ~params,
              colors = "Accent",
              type = "scatter",
              mode = "lines") %>%
      plotly::layout(
        title = "",
        xaxis = list(
          title = "Number of fibres"
        ),
        yaxis = list(
          title = "LR"
        ),
        margin = list(
          t = 40
        ),
        autosize = TRUE
      )
```

